\textbf{Supplementary Information}

### 2020-03-20 submission/supplementary.tex
References update.

\caption{Rarefaction curves of bacterial and archaeal communities from the surfaces of macrophytes (\textit{C. nodosa} [Mixed] and \textit{C. cylindracea} [Mixed and Monospecific]) and in the ambient seawater.\label{rarefaction}}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\caption{Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of macrophytes (\textit{C. nodosa} [Mixed] and \textit{C. cylindracea} [Mixed and Monospecific]) and in the ambient seawater.\label{calculators}}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Relative contribution of chloroplast sequences on the surfaces of macrophytes (\textit{C. nodosa} [Mixed] and \textit{C. cylindracea} [Mixed and Monospecific]) and in the ambient seawater.\label{chloroplast}}\label{fig:unnamed-chunk-3}
\end{figure}

@@

3 & Seawater & 13 July 2017 & Summer & 25,996 & 821\\
5 & Seawater & 27 July 2017 & Summer & 58,954 & 993\\
7 & Seawater & 10 August 2017 & Summer & 32,626 & 853\\
9 & Seawater & 24 August 2017 & Summer & 60,935 & 1,064\\
11 & Seawater & 19 September 2017 & Summer & 46,107 & 1,179\\
13 & Seawater & 12 October 2017 & Autumn & 30,911 & 971\\
15 & Seawater & 23 November 2017 & Autumn & 27,585 & 1,197\\
17 & Seawater & 14 December 2017 & Autumn & 44,595 & 2,275\\
19 & Seawater & 13 February 2018 & Winter & 44,207 & 1,306\\
21 & Seawater & 27 March 2018 & Winter & 46,313 & 1,561\\
23a & Seawater & 24 April 2018 & Spring & 30,973 & 999\\
23b & Seawater & 24 April 2018 & Spring & 38,563 & 1,195\\
25 & Seawater & 22 May 2018 & Spring & 53,877 & 1,787\\
27 & Seawater & 19 June 2018 & Spring & 77,465 & 1,290\\
29 & Seawater & 10 July 2018 & Summer & 50,793 & 1,445\\
31 & Seawater & 9 August 2018 & Summer & 39,041 & 1,123\\
33 & Seawater & 4 September 2018 & Summer & 36,206 & 1,206\\
35 & Seawater & 5 October 2018 & Autumn & 49,585 & 1,019\\
37 & \textit{Cymodocea nodosa} (Mixed) & 23 November 2017 & Autumn & 31,237 & 1,555\\
41 & \textit{Cymodocea nodosa} (Mixed) & 4 December 2017 & Autumn & 24,234 & 1,174\\
45 & \textit{Cymodocea nodosa} (Mixed) & 14 December 2017 & Autumn & 32,683 & 1,061\\
49 & \textit{Cymodocea nodosa} (Mixed) & 13 February 2018 & Winter & 9,088 & 1,216\\
52 & \textit{Cymodocea nodosa} (Mixed) & 27 March 2018 & Winter & 17,005 & 1,216\\
55 & \textit{Cymodocea nodosa} (Mixed) & 24 April 2018 & Spring & 42,645 & 2,053\\
58 & \textit{Cymodocea nodosa} (Mixed) & 22 May 2018 & Spring & 21,337 & 1,290\\
61 & \textit{Cymodocea nodosa} (Mixed) & 19 June 2018 & Spring & 31,726 & 2,098\\
64 & \textit{Cymodocea nodosa} (Mixed) & 10 July 2018 & Summer & 35,729 & 1,793\\
67 & \textit{Cymodocea nodosa} (Mixed) & 9 August 2018 & Summer & 26,356 & 2,116\\
70 & \textit{Cymodocea nodosa} (Mixed) & 4 September 2018 & Summer & 23,275 & 1,724\\
73 & \textit{Cymodocea nodosa} (Mixed) & 5 October 2018 & Autumn & 29,907 & 2,211\\
38 & \textit{Caulerpa cylindracea} (Mixed) & 23 November 2017 & Autumn & 36,309 & 2,896\\
42 & \textit{Caulerpa cylindracea} (Mixed) & 4 December 2017 & Autumn & 28,383 & 3,249\\
46 & \textit{Caulerpa cylindracea} (Mixed) & 14 December 2017 & Autumn & 34,718 & 3,067\\
53 & \textit{Caulerpa cylindracea} (Mixed) & 27 March 2018 & Winter & 28,689 & 2,481\\
56 & \textit{Caulerpa cylindracea} (Mixed) & 24 April 2018 & Spring & 34,784 & 3,057\\
59 & \textit{Caulerpa cylindracea} (Mixed) & 22 May 2018 & Spring & 23,392 & 2,712\\
62 & \textit{Caulerpa cylindracea} (Mixed) & 19 June 2018 & Spring & 36,488 & 3,311\\
65 & \textit{Caulerpa cylindracea} (Mixed) & 10 July 2018 & Summer & 18,483 & 2,188\\
68 & \textit{Caulerpa cylindracea} (Mixed) & 9 August 2018 & Summer & 31,943 & 3,097\\
71 & \textit{Caulerpa cylindracea} (Mixed) & 4 September 2018 & Summer & 29,273 & 3,152\\
74 & \textit{Caulerpa cylindracea} (Mixed) & 5 October 2018 & Autumn & 11,707 & 1,711\\
39 & \textit{Caulerpa cylindracea} (Monospecific) & 23 November 2017 & Autumn & 22,057 & 2,428\\

@@

47 & \textit{Caulerpa cylindracea} (Monospecific) & 14 December 2017 & Autumn & 8,409 & 1,451\\
51 & \textit{Caulerpa cylindracea} (Monospecific) & 13 February 2018 & Winter & 11,673 & 1,899\\
54 & \textit{Caulerpa cylindracea} (Monospecific) & 27 March 2018 & Winter & 39,471 & 3,142\\
57 & \textit{Caulerpa cylindracea} (Monospecific) & 24 April 2018 & Spring & 20,304 & 2,836\\
60 & \textit{Caulerpa cylindracea} (Monospecific) & 22 May 2018 & Spring & 33,035 & 3,314\\
63 & \textit{Caulerpa cylindracea} (Monospecific) & 19 June 2018 & Spring & 41,841 & 3,976\\
66 & \textit{Caulerpa cylindracea} (Monospecific) & 10 July 2018 & Summer & 27,038 & 2,669\\
69 & \textit{Caulerpa cylindracea} (Monospecific) & 9 August 2018 & Summer & 26,734 & 3,123\\
72 & \textit{Caulerpa cylindracea} (Monospecific) & 4 September 2018 & Summer & 31,874 & 3,248\\
75 & \textit{Caulerpa cylindracea} (Monospecific) & 5 October 2018 & Autumn & 33,073 & 3,078\\*

>>>>

\caption{Rarefaction curves of bacterial and archaeal communities from the surfaces of macrophytes (\textit{C. nodosa} [Mixed Settlement] and \textit{C. cylindracea} [Mixed and Monospecific Settlement]) and in the ambient seawater.\label{rarefaction}}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\caption{Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of macrophytes (\textit{C. nodosa} [Mixed Settlement] and \textit{C. cylindracea} [Mixed and Monospecific Settlement]) and in the ambient seawater.\label{calculators}}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Relative contribution of chloroplast sequences on the surfaces of macrophytes (\textit{C. nodosa} [Mixed Settlement] and \textit{C. cylindracea} [Mixed and Monospecific Settlement]) and in the ambient seawater.\label{chloroplast}}\label{fig:unnamed-chunk-3}
\end{figure}

@@

3 & Seawater & 13 July 2017 & Summer & 25,996 & 824\\
5 & Seawater & 27 July 2017 & Summer & 58,950 & 989\\
7 & Seawater & 10 August 2017 & Summer & 32,631 & 851\\
9 & Seawater & 24 August 2017 & Summer & 60,935 & 1,060\\
11 & Seawater & 19 September 2017 & Summer & 46,115 & 1,170\\
13 & Seawater & 12 October 2017 & Autumn & 30,913 & 973\\
15 & Seawater & 23 November 2017 & Autumn & 27,586 & 1,187\\
17 & Seawater & 14 December 2017 & Autumn & 44,584 & 2,270\\
19 & Seawater & 13 February 2018 & Winter & 44,185 & 1,313\\
21 & Seawater & 27 March 2018 & Winter & 46,375 & 1,573\\
23a & Seawater & 24 April 2018 & Spring & 30,968 & 996\\
23b & Seawater & 24 April 2018 & Spring & 38,572 & 1,200\\
25 & Seawater & 22 May 2018 & Spring & 53,871 & 1,796\\
27 & Seawater & 19 June 2018 & Spring & 77,463 & 1,292\\
29 & Seawater & 10 July 2018 & Summer & 50,811 & 1,444\\
31 & Seawater & 9 August 2018 & Summer & 39,051 & 1,120\\
33 & Seawater & 4 September 2018 & Summer & 36,200 & 1,202\\
35 & Seawater & 5 October 2018 & Autumn & 49,568 & 1,012\\
37 & \textit{Cymodocea nodosa} (Mixed) & 23 November 2017 & Autumn & 31,236 & 1,552\\
41 & \textit{Cymodocea nodosa} (Mixed) & 4 December 2017 & Autumn & 24,252 & 1,184\\
45 & \textit{Cymodocea nodosa} (Mixed) & 14 December 2017 & Autumn & 32,681 & 1,053\\
49 & \textit{Cymodocea nodosa} (Mixed) & 13 February 2018 & Winter & 9,089 & 1,213\\
52 & \textit{Cymodocea nodosa} (Mixed) & 27 March 2018 & Winter & 17,002 & 1,211\\
55 & \textit{Cymodocea nodosa} (Mixed) & 24 April 2018 & Spring & 42,642 & 2,058\\
58 & \textit{Cymodocea nodosa} (Mixed) & 22 May 2018 & Spring & 21,337 & 1,294\\
61 & \textit{Cymodocea nodosa} (Mixed) & 19 June 2018 & Spring & 31,724 & 2,111\\
64 & \textit{Cymodocea nodosa} (Mixed) & 10 July 2018 & Summer & 35,738 & 1,794\\
67 & \textit{Cymodocea nodosa} (Mixed) & 9 August 2018 & Summer & 26,355 & 2,119\\
70 & \textit{Cymodocea nodosa} (Mixed) & 4 September 2018 & Summer & 23,275 & 1,723\\
73 & \textit{Cymodocea nodosa} (Mixed) & 5 October 2018 & Autumn & 29,911 & 2,216\\
38 & \textit{Caulerpa cylindracea} (Mixed) & 23 November 2017 & Autumn & 36,311 & 2,886\\
42 & \textit{Caulerpa cylindracea} (Mixed) & 4 December 2017 & Autumn & 28,381 & 3,235\\
46 & \textit{Caulerpa cylindracea} (Mixed) & 14 December 2017 & Autumn & 34,724 & 3,074\\
53 & \textit{Caulerpa cylindracea} (Mixed) & 27 March 2018 & Winter & 28,694 & 2,483\\
56 & \textit{Caulerpa cylindracea} (Mixed) & 24 April 2018 & Spring & 34,780 & 3,061\\
59 & \textit{Caulerpa cylindracea} (Mixed) & 22 May 2018 & Spring & 23,393 & 2,720\\
62 & \textit{Caulerpa cylindracea} (Mixed) & 19 June 2018 & Spring & 36,491 & 3,316\\
65 & \textit{Caulerpa cylindracea} (Mixed) & 10 July 2018 & Summer & 18,485 & 2,186\\
68 & \textit{Caulerpa cylindracea} (Mixed) & 9 August 2018 & Summer & 31,956 & 3,112\\
71 & \textit{Caulerpa cylindracea} (Mixed) & 4 September 2018 & Summer & 29,273 & 3,153\\
74 & \textit{Caulerpa cylindracea} (Mixed) & 5 October 2018 & Autumn & 11,692 & 1,703\\
39 & \textit{Caulerpa cylindracea} (Monospecific) & 23 November 2017 & Autumn & 22,081 & 2,432\\

@@

47 & \textit{Caulerpa cylindracea} (Monospecific) & 14 December 2017 & Autumn & 8,409 & 1,454\\
51 & \textit{Caulerpa cylindracea} (Monospecific) & 13 February 2018 & Winter & 11,674 & 1,908\\
54 & \textit{Caulerpa cylindracea} (Monospecific) & 27 March 2018 & Winter & 39,470 & 3,133\\
57 & \textit{Caulerpa cylindracea} (Monospecific) & 24 April 2018 & Spring & 20,296 & 2,833\\
60 & \textit{Caulerpa cylindracea} (Monospecific) & 22 May 2018 & Spring & 33,034 & 3,315\\
63 & \textit{Caulerpa cylindracea} (Monospecific) & 19 June 2018 & Spring & 41,842 & 3,970\\
66 & \textit{Caulerpa cylindracea} (Monospecific) & 10 July 2018 & Summer & 27,040 & 2,675\\
69 & \textit{Caulerpa cylindracea} (Monospecific) & 9 August 2018 & Summer & 26,735 & 3,120\\
72 & \textit{Caulerpa cylindracea} (Monospecific) & 4 September 2018 & Summer & 31,871 & 3,264\\
75 & \textit{Caulerpa cylindracea} (Monospecific) & 5 October 2018 & Autumn & 33,077 & 3,078\\*
